\textbf{ Accurate spectrophotometric estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-07-31 paper/sp.tex
validation tests

We adopt 9~percent as the method's precision.
This estimate is conservative in that the 9-percent scatter includes contributions
from both our spectrophotometric model and from the \gaia\ measurements themselves.
However this estimate is not so conservative in that the test is performed with
\gaia's best stars, which are bright, nearby, in low extinction regions, and
(because of these things) near Solar metallicity.
There could in principle be additional bias or scatter for stars that are in dustier
regions or at lower metallicities.
\figurename~HOGG WHAT FIGURE shows that
there is no suggestion of any such trends when we color the residuals by metallicity
or $H-W_2$ (which is a reddening proxy).

HOGG: validation with clusters and Sag.

Brief comment on the flexibility of the photometric model and interpretation of the photometric coefficients. Maybe plot some photometric properties vs metallicity or dust?

>>>>

We adopt 9~percent as the method's precision.
This estimate is conservative in that the 9-percent scatter includes contributions
from both our spectrophotometric model and from the \gaia\ measurements themselves.
However this estimate is not so conservative in that the test is performed with
\gaia's best stars, which are bright, nearby, in low extinction regions, and
(because of these things) near Solar metallicity.
There could in principle be additional bias or scatter for stars that are in dustier
regions or at lower metallicities.
\figurename~HOGG WHAT FIGURE shows that
there is no suggestion of any such trends when we color the residuals by metallicity
or $H-W_2$ color (which is a reddening proxy).

Another validation of the results can be obtained by looking at known
clusters or spatially compact objects in the data.
In HOGG WHAT FIGURE, we show the parallax distribution from \gaia\ and
the spectroscopic-parallax distribution from this work for stars in
angular proximity to known stellar clusters and the Sagittarius dwarf
galaxy.
These clusters span some range in metallicity and age, and therefore test
the accuracy of the method for different kinds of populations.
They show that both \gaia\ and the spectroscopic parallaxes appear to be unbiased
for these clusters and the range in abundances and ages they represent.
HOGG: DO WE NEED TO ADDRESS whether why not these clusters show 9-percent spreads?

HOGG: Brief comment on the flexibility of the photometric model and interpretation of the photometric coefficients. Maybe plot some photometric properties vs metallicity or dust?
